Abstract Binding Trees

### 2015-10-25 paper.tex
Bold the category C so it doesn't look like an object

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Of{\Psi}{C\to\Sets}$ but we keep the
  $C$ implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $\IMode{C\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in C}\Coslice{c}{C}
    \otimes \Discrete{\Psi(c)}}$.}
$\Of{\Grothendieck{}{(-)}}{\Sets^{C}\to\Cats}$ on operators, we have a category
of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$ for
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{\Pair{\varrho}{f}}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such
that
$\EqMember{\Lift{\varrho}{f}(\vartheta)}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck opfibration and $\Forget{-}_{\Singleton}$ is the forgetful functor
from pointed sets:

@@

Because we have not committed to using the built-in binding machinery to
express the well-scopedness of telescopes and sequents, we are free to use
\emph{symbols} in order to model the variables in the context. This is actually
quite sensible if we are trying to actually faithfully represent the syntax of
telescopes and sequents, rather than replace them with their counterparts on the
meta-level. It is certainly not intended that we should be able to take a
context $\Match{H}{x:A}$ and apply the substitution
$\IsSubst{M}{x}{H}{M:A}$, which is nonsensical; on the other hand, if $x$
had been a \emph{symbol}, all we could do is rename it in the context, since
substitution is not defined for symbols.

>>>>

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $\mathbf{C}\Grothendieck{}{\Psi}$
  represents the category of elements of a copresheaf
  $\Of{\Psi}{\mathbf{C}\to\Sets}$ but we keep the $\mathbf{C}$ implicit and
  simply refer to it as the Grothendieck construction.  Alternatively, this
  construction can be understood as a coend
$\IMode{\mathbf{C}\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in
\mathbf{C}}\Coslice{c}{\mathbf{C}} \otimes \Discrete{\Psi(c)}}$.}
$\Of{\Grothendieck{}{(-)}}{\Sets^{\mathbf{C}}\to\Cats}$ on operators, we have a
category of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{\Pair{\varrho}{f}}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such
that
$\EqMember{\Lift{\varrho}{f}(\vartheta)}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck opfibration and $\Forget{-}_{\Singleton}$ is the forgetful functor
from pointed sets:

@@

Because we have not committed to using the built-in binding machinery to
express the well-scopedness of telescopes and sequents, we are free to use
\emph{symbols} in order to model the variables in the context. This is in fact
quite sensible if we are actually trying to faithfully represent the syntax of
telescopes and sequents, rather than replace them with their counterparts on
the meta-level. It is certainly not intended that we should be able to take a
context $\Match{H}{x:A}$ and apply the substitution $\IsSubst{M}{x}{H}{M:A}$,
which is nonsensical; on the other hand, if $x$ had been a \emph{symbol}, all
we could do is rename it in the context, since substitution is not defined for
symbols.
